Interpolate the weight at agecl output to annual age

### 2020-06-05 InterpolateWeightAtAge.Rmd
three species all but the oldest ages

```{r interp-wtage-test1}

@@

New omdimensions file:
```{r, code = readLines("./config/omdimenstions.R"), eval=F}
```

@@

```{r indcomp-test}

@@

```{r comps-redo, message=FALSE}

@@

@@

# plot portion, just redfish, capelin is blank and cod looks the same
library(ggforce)
NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=3, scales = "free")

@@

# dataframe portion
intwtCod <- NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "North_atl_cod")

intwtRed <- NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "Redfish")

intwtCap <- NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "Capelin") #empty

wtageCod <- NOBAom_redcodcap_comp$survObsWtAtAge[[1]] %>%
  filter(species == "North_atl_cod")

wtageRed <- NOBAom_redcodcap_comp$survObsWtAtAge[[1]] %>%
  filter(species == "Redfish")

wtageCap <- NOBAom_redcodcap_comp$survObsWtAtAge[[1]] %>%
  filter(species == "Capelin")

@@

  wtagep <- ggplot(wtagecl, aes(agecl, atoutput)) +
    geom_point() +
    geom_line(aes(colour = factor(time))) + 
    scale_x_continuous(minor_breaks = c(0:max(agecl))) +
    theme_tufte() +
    theme(legend.position = "none",
          panel.grid.minor.x = element_line(colour = "grey50"),
          panel.grid.major.x = element_line(colour = "grey50"))

@@

>>>>

```{r interp-wtage-test1, eval=FALSE}

@@

New omdimensions file:
```{r, code = readLines("./config/omdimensions.R"), eval=F}
```

@@

```{r indcomp-test, eval=FALSE}

@@

```{r comps-redo, message=FALSE, eval=FALSE}

@@

```{r readin-savedoutput}

survObsFullWtAtAge <- readRDS(file.path(d.name, paste0(scenario.name, "survObsFullWtAtAge.rds")))

survObsWtAtAge <- readRDS(file.path(d.name, paste0(scenario.name, "survObsWtAtAge.rds")))

NOBAom_redcodcap <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))

@@

# plot portion, just redfish, capelin is blank and cod looks the same
library(ggforce)
survObsFullWtAtAge[[1]][[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=3, scales = "free")

@@

# dataframe portion
intwtCod <- survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "North_atl_cod")

intwtRed <- survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "Redfish")

intwtCap <- survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "Capelin") #empty, no need for interpolation, but make intelligent

wtageCod <- survObsWtAtAge[[1]] %>%
  filter(species == "North_atl_cod")

wtageRed <- survObsWtAtAge[[1]] %>%
  filter(species == "Redfish")

wtageCap <- survObsWtAtAge[[1]] %>%
  filter(species == "Capelin")

@@

  wtagep <- ggplot(wtagecl, aes(agecl, atoutput)) +
    geom_point() +
    geom_line(aes(colour = factor(time))) + 
    scale_x_continuous(minor_breaks = c(0:max(wtagecl$agecl))) +
    theme_tufte() +
    theme(legend.position = "none",
          panel.grid.minor.x = element_line(colour = "grey50"),
          panel.grid.major.x = element_line(colour = "grey50"))

wtagep

@@

Capelin is fine with WtAtAge output because it has age classes = true ages!
Maybe just warn that a species with fgs$NumAgeClassSize = 1 will have NA output of interpolation functions, which will run if there is output for that species in the ANNAGEBIO.nc and ANNAGECATCH.nc files.

Redfish appear to have *decreasing* average weight at age as they get older:

```{r redfish-1}

wtagecl <- wtageRed

  wtagep <- ggplot(wtagecl, aes(agecl, atoutput)) +
    geom_point() +
    geom_line(aes(colour = factor(time))) + 
    scale_x_continuous(minor_breaks = c(0:max(wtagecl$agecl))) +
    theme_tufte() +
    theme(legend.position = "none",
          panel.grid.minor.x = element_line(colour = "grey50"),
          panel.grid.major.x = element_line(colour = "grey50"))

wtagep

Diagnose Redfish problem (it was not negative increments, but inadequate lagging and leading):

```{r redfishdebug, message=FALSE}

annageRed <- NOBAom_redcodcap$truenumsage_ss %>%
  filter(species == "Redfish")

annageCod <- NOBAom_redcodcap$truenumsage_ss %>%
  filter(species == "North_atl_cod")

annageCap <- NOBAom_redcodcap$truenumsage_ss %>%
  filter(species == "Capelin")

annages <- annageRed
wtagecl <- wtageRed
fgs <- fgs

  annages <- annages %>%
    group_by(species, time, agecl) %>%
    rename(trueage = agecl) %>%
    summarise(truenatage = sum(atoutput))

  # assuming fgs is data object already been read in by load_fgs elsewhere
  # Figure out the groups that have multiple ages classes in each stage (or
  # cohort)
  multiple_ages <- fgs[fgs$NumAgeClassSize>1, c(1,4,10)]

  # make a dataframe the right dimensions for all age classes
  # has species, time from wtage and trueage, truenatage from annages
  # add agecl column
  # finds the average age of each agecl each timestep based on truenatage
  wtage_out <- annages %>%
    dplyr::semi_join(wtagecl, by = c("species", "time")) %>%
    dplyr::inner_join(multiple_ages, by = c("species" = "Name")) %>%
    dplyr::mutate(agecl = as.integer(ceiling(trueage/NumAgeClassSize))) %>%
    dplyr::group_by(species, time, agecl) %>%
    dplyr::mutate(avgage = weighted.mean(trueage, truenatage))

  # complex, but works for 2 ages/agecl, need to test more, need to fix oldest
  # for more than 2 ages/agecl need to have a bigger lead/lag
  # achieved by faking a scalar for lead/lag n using max() function
  # should be ceiling I think for odd NumAgeClassSize, but not sure?
  wtage_out <- wtage_out %>%
    dplyr::select(species, time, trueage, NumAgeClassSize, agecl, avgage) %>%
    dplyr::left_join(wtagecl_inc) %>%
    dplyr::group_by(species, time) %>%
    dplyr::mutate(wtIntage = case_when(
      (agecl==1 & trueage<avgage) ~ (1-(avgage-trueage)/avgageinc)*increment,
      (agecl>1 & trueage<avgage) ~
        (1-(avgage-trueage)/avgageinc)*increment +
        lag(atoutput, ceiling(max(NumAgeClassSize)/2)),
      (trueage>avgage) ~
        ((trueage-avgage)/lead(avgageinc, ceiling(max(NumAgeClassSize)/2)))*lead(increment, ceiling(max(NumAgeClassSize)/2)) + atoutput
    ))

  # diagnostic plot--are interpolations where we expect them?
  wtageclann <- ggplot(wtagecl_inc, aes(avgage, atoutput)) +
    geom_point() +
    geom_line(aes(colour = factor(time))) +
    scale_x_continuous(minor_breaks = c(0:max(wtage_out$trueage))) +
    theme_tufte() +
    theme(legend.position = "none",
          panel.grid.minor.x = element_line(colour = "grey50"),
          panel.grid.major.x = element_line(colour = "grey50"))

  diag.p <- wtageclann + geom_point(data = wtage_out,
                          mapping = aes(trueage, wtIntage))

  # #clean up to have only standard columns
  # finaldata <- data.frame("species" = wtage_out$species,
  #                         "agecl" = wtage_out$trueage, "polygon" = NA, "layer" = NA,
  #                         "time" = wtage_out$time, "atoutput" = wtage_out$wtIntage)

  diag.p

Try the updated function again, any bugs with multiple species? OK so far.

```{r test-correctedinterp, warning=FALSE, message=FALSE}

omlist_ss <- NOBAom_redcodcap

interp_survWtAtAge <- calc_avgwtstage2age(wtagecl = survObsWtAtAge[[1]],
                                                     annages = omlist_ss$truenumsage_ss,
                                                     fgs = omlist_ss$funct.group_ss)

interp_survWtAtAge[[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=1, scales = "free")

interp_survWtAtAge[[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=2, scales = "free")

interp_survWtAtAge[[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=3, scales = "free")

Last issue is extrapolating the oldest wt at age. Linear from the last one?
